---
title: "RegressionAnalysis"
author: "qy"
knit: (function(inputFile, encoding) {
      out_dir <- "../docs/age";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
output:
  html_document:
    theme: journal
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Preparation

Here we want to analyze the difference of voices between genders. 

```{r}
voice = read.csv("../../data/regression/balanced_train.csv")
X <- voice[, !(colnames(voice) %in% c("gender"))]
y <- voice$gender
y <- ifelse(y == "male", 0, 1)
head(voice)
```

```{r}
# install.packages("caret")
library(caret)
set.seed(42)

# Split the data into training and testing sets
train_indices <- createDataPartition(y, p = 0.8, list = FALSE)
X_train <- X[train_indices, ]
X_test <- X[-train_indices, ]
y_train <- y[train_indices]
y_test <- y[-train_indices]

```

## Correlation

We select the following columns for correlation analysis, as we assume they would highly correlate with each other. We plot the heatmap as follows:


```{r}
# install.packages("corrplot")
library(corrplot)

distribution_cols <- c("meanfreq", "median", "Q25", "Q75", "meandom")

correlation_matrix <- cor(voice[, distribution_cols])

corrplot(correlation_matrix, method = "color", type = "upper", 
         addCoef.col = "black", tl.col = "black", tl.srt = 45,
         diag = FALSE)

```

```{r}
# install.packages("GGally")
library(GGally)
library(ggplot2)

# Save the plot to a PDF file
pdf("../../report/graphs/scatter_matrix.pdf", width = 7, height = 7)
ggpairs(voice, columns = distribution_cols, 
        mapping = ggplot2::aes(color = gender),
        lower = list(continuous = wrap("points", size = 0.1)),
        diag = list(continuous = wrap("barDiag", size = 0.1)))
dev.off()
```


## Simple Linear Regression

We first perform simple linear regression

### Relationship between mean frequency and meanfun

```{r}
cor.test(voice$meanfreq, voice$meanfun)
```


```{r}
model1 <- lm(voice$meanfreq ~ voice$meanfun)
summary(model1)
model1$coefficients
confint(model1, level = 0.95)
```

To viualise the relationship between mean frequency and meanfun, we plot the scatter plot as follows:

```{r}
plot(voice$meanfun, voice$meanfreq, 
     xlab = "Mean Fundamental Frequency", ylab = "Mean Frequency",
     main = "Scatter Plot with Regression Line")
abline(model1, col = "red")
```

### Relationship between mean frequency and meandom

```{r}
cor.test(voice$meanfreq, voice$meandom)
```

```{r}
model2 <- lm(voice$meanfreq ~ voice$meandom)
summary(model2)
model2$coefficients
confint(model2, level = 0.95)
```

To viualise the relationship between mean frequency and meandom, we plot the scatter plot as follows:

```{r}
plot(voice$meandom, voice$meanfreq, 
     xlab = "Meandom", ylab = "Mean Frequency",
     main = "Scatter Plot with Regression Line")
abline(model2, col = "red")
```

### Relationship between mean frequency and mindom

```{r}
cor.test(voice$meanfreq, voice$mindom)
```

```{r}
model3 <- lm(voice$meanfreq ~ voice$mindom)
summary(model3)
model3$coefficients
confint(model3, level = 0.95)
```

To viualise the relationship between mean frequency and mindom, we plot the scatter plot as follows:

```{r}
plot(voice$mindom, voice$meanfreq, 
     xlab = "Mindom", ylab = "Mean Frequency",
     main = "Scatter Plot with Regression Line")
abline(model3, col = "red")
```


### Relationship between mean frequency and maxdom

```{r}
cor.test(voice$meanfreq, voice$maxdom)
```

```{r}
model4 <- lm(voice$meanfreq ~ voice$maxdom)
summary(model4)
model4$coefficients
confint(model4, level = 0.95)
```

To viualise the relationship between mean frequency and maxdom, we plot the scatter plot as follows:

```{r}
plot(voice$maxdom, voice$meanfreq, 
     xlab = "Maxdom", ylab = "Mean Frequency",
     main = "Scatter Plot with Regression Line")
abline(model4, col = "red")
```

## Multiple Linear Regression

We then perform multiple linear regression, finding the relationship between mean frequency and meanfun, meandom, mindom, and maxdom.

```{r}
model <- lm(meanfreq ~ meanfun + meandom + mindom + maxdom, data = voice)
step(model, direction="backward")
```

## Logistic Regression

Logistic regression models the probability that Gender belong to "male" or "female". 


```{r}
model <- glm(y_train ~ ., data = cbind(y_train, X_train), family = binomial)

print(paste("beta_0:", coef(model)[1]))
print(paste("beta_1:", coef(model)[2]))

train_pred <- predict(model, newdata = X_train, type = "response")
train_accuracy <- mean(ifelse(train_pred > 0.5, 1, 0) == y_train)
print(paste("Training set accuracy:", train_accuracy))

test_pred <- predict(model, newdata = X_test, type = "response")
test_accuracy <- mean(ifelse(test_pred > 0.5, 1, 0) == y_test)
print(paste("Test set accuracy:", test_accuracy))

conf_matrix <- table(ifelse(test_pred > 0.5, 1, 0), y_test)
print(conf_matrix)

TPR_logreg_1 <- conf_matrix[2, 2] / sum(conf_matrix[2, ])
print(paste("True Positive Rate:", TPR_logreg_1))

TNR_logreg_1 <- conf_matrix[1, 1] / sum(conf_matrix[1, ])
print(paste("True Negative Rate:", TNR_logreg_1))

FPR_logreg_1 <- conf_matrix[1, 2] / sum(conf_matrix[1, ])
print(paste("False Positive Rate:", FPR_logreg_1))

FNR_logreg_1 <- conf_matrix[2, 1] / sum(conf_matrix[2, ])
print(paste("False Negative Rate:", FNR_logreg_1))
```

## K-Nearest Neighbors

```{r}
library(class)
library(caret)

knn_model <- knn(train = X_train, test = X_test, cl = y_train, k = 1)

train_accuracy <- sum(knn_model == y_train) / length(y_train)
print(paste("Training set accuracy:", train_accuracy))

test_accuracy <- sum(knn_model == y_test) / length(y_test)
print(paste("Test set accuracy:", test_accuracy))

conf_matrix <- table(Actual = y_test, Predicted = knn_model)
print(conf_matrix)

TP <- conf_matrix[2, 2]  # True Positives
TN <- conf_matrix[1, 1]  # True Negatives
FP <- conf_matrix[1, 2]  # False Positives
FN <- conf_matrix[2, 1]  # False Negatives

TPR_knn <- TP / (TP + FN)  
TNR_knn <- TN / (TN + FP)  
FPR_knn <- FP / (FP + TN)  
FNR_knn <- FN / (FN + TP)  

print(paste("True Positive Rate:", TPR_knn))
print(paste("True Negative Rate:", TNR_knn))
print(paste("False Positive Rate:", FPR_knn))
print(paste("False Negative Rate:", FNR_knn))
```