---
title: "Analysis"
knit: (function(inputFile, encoding) {
      out_dir <- "../docs/report/graph";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir),
                        output_format = "pdf_document")})
output:
  html_document:
    theme: journal
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
MALE_COLOR <- rgb(0, 0, 1, 0.2)
FEMALE_COLOR <- rgb(1, 0, 0, 0.2)
```

# Data Preparation

```{r, out.width="50%", fig.align = 'center'}
voice <- read.csv("../../data/gender/balanced_train.csv")
head(voice)
```

```{r, out.width="50%", fig.align = 'center'}
male_data <- voice[voice$gender == "male", ]
female_data <- voice[voice$gender == "female", ]
head(male_data)
head(female_data)
```

# Data Analysis

## Gender

```{r, out.width="50%", fig.align = 'center'}
pie(table(voice$gender), main = "Male and Female")
```

```{r, out.width="50%", fig.align = 'center'}
visualize_data <- function(column) {
  # return(male_data[column])
  hist(male_data[[column]], xlab = column, col = MALE_COLOR, prob = TRUE, breaks = 80, border = "white", main = sprintf("Histogram and KDE of %s", column))
  hist(female_data[[column]], xlab = column, col = FEMALE_COLOR, prob = TRUE, add = TRUE, breaks = 80, border = "white")

  # Calculate and plot KDE for male data
  male_density <- density(male_data[[column]])
  lines(male_density, col = "blue", lwd = 2)

  # Calculate and plot KDE for female data
  female_density <- density(female_data[[column]])
  lines(female_density, col = "red", lwd = 2)

  legend("topright", legend = c("Male", "Female"), col = c("blue", "red"), lwd = 2, fill = c(MALE_COLOR, FEMALE_COLOR))
}
```

```{r, out.width="30%", fig.align = 'center'}
pdf("../../docs/report/graphs/gender/visualizations.pdf", width = 13, height = 10)
par(mfrow = c(3, 3))

column_names <- colnames(voice)[-which(colnames(voice) == "gender")]
for (column in column_names) {
  visualize_data(column)
}

dev.off()
```

```{r, out.width="30%", fig.align = 'center'}
pdf("../../docs/report/graphs/gender/qq_plot_male.pdf", width = 10, height = 10)
par(mfrow = c(3, 3))

column_names <- colnames(voice)[-which(colnames(voice) == "gender")]
for (column in column_names) {
  qqnorm(voice[voice$gender == "male", column], main = column)
  qqline(voice[voice$gender == "male", column], col = "red")
}

dev.off()
```

```{r, out.width="30%", fig.align = 'center'}
pdf("../../docs/report/graphs/gender/qq_plot_female.pdf", width = 10, height = 10)
par(mfrow = c(3, 3))

column_names <- colnames(voice)[-which(colnames(voice) == "gender")]
for (column in column_names) {
  qqnorm(voice[voice$gender == "female", column], main = column)
  qqline(voice[voice$gender == "female", column], col = "red")
}

dev.off()
```

## Mean Frequency

### Visualizing the data

We first visualize the data by plotting the histogram 

```{r, out.width="30%", fig.align = 'center'}
visualize_data("meanfreq")
```

```{r, out.width="30%", fig.align = 'center'}
variable <- "meanfreq"
boxplot(male_data[[variable]], female_data[[variable]])
```

### QQ-plot

We then plot the QQ-plot to check for normality

```{r, out.width="50%", fig.align = 'center'}
qqnorm(male_data$meanfreq)
qqline(male_data$meanfreq, col = "red")


qqnorm(female_data$meanfreq)
qqline(female_data$meanfreq, col = "red")

shapiro.test(male_data$meanfreq)
shapiro.test(female_data$meanfreq)
```

Based on the QQ-plot, we can see that the data is normally distributed. We would therefore use the F test to compare the variance of the data

### F-test

```{r, out.width="50%", fig.align = 'center'}
var.test(male_data$meanfreq, female_data$meanfreq)
```

Since the p-value is less than 0.05, we reject the null hypothesis that the variance of the data is the same, we would therefore use the two sample t-test with unequal variance

### Two Sample T-test

```{r, out.width="50%", fig.align = 'center'}
t.test(male_data$meanfreq, female_data$meanfreq, var.equal = FALSE)
```
Since the p-value is greater than 0.05, we do not reject the null hypothesis that the mean of the data is the same

## Q25

### Visualizing the data

We first visualize the data by plotting the histogram 

```{r, out.width="50%", fig.align = 'center'}
visualize_data("Q25")
```

```{r, out.width="50%", fig.align = 'center'}
variable <- "Q25"
boxplot(male_data[[variable]], female_data[[variable]])
```

### QQ-plot

We then plot the QQ-plot to check for normality

```{r, out.width="50%", fig.align = 'center'}
qqnorm(male_data$Q25)
qqline(male_data$Q25, col = "red")


qqnorm(female_data$Q25)
qqline(female_data$Q25, col = "red")
```

Based on the QQ-plot, we can see that the data is not normally distributed. We would therefore use the Wilcoxon test to compare the mean of the data

### Wilcoxon Test

```{r, out.width="50%", fig.align = 'center'}
wilcox.test(male_data$Q25, female_data$Q25, alt = "less")
```

The p-value is less than 0.05, we reject the null hypothesis that the mean of the data is the same

## Q75

### Visualizing the data

We first visualize the data by plotting the histogram 

```{r, out.width="50%", fig.align = 'center'}
visualize_data("Q75")
```

```{r, out.width="50%", fig.align = 'center'}
variable <- "Q75"
boxplot(male_data[[variable]], female_data[[variable]])
```

### QQ-plot

We then plot the QQ-plot to check for normality

```{r, out.width="50%", fig.align = 'center'}
qqnorm(male_data$Q75)
qqline(male_data$Q75, col = "red")


qqnorm(female_data$Q75)
qqline(female_data$Q75, col = "red")
```

Based on the QQ-plot, we can see that the data is not normally distributed. We would therefore use the Wilcoxon test to compare the mean of the data

### Wilcoxon Test

```{r, out.width="50%", fig.align = 'center'}
wilcox.test(male_data$Q75, female_data$Q75, alt = "less")
```

The p-value is more than 0.05, we do not reject the null hypothesis that the mean of the data is the same

## median

### Visualizing the data

We first visualize the data by plotting the histogram 

```{r, out.width="50%", fig.align = 'center'}
visualize_data("median")
```

```{r, out.width="50%", fig.align = 'center'}
variable <- "median"
boxplot(male_data[[variable]], female_data[[variable]])
```

### QQ-plot

We then plot the QQ-plot to check for normality

```{r, out.width="50%", fig.align = 'center'}
qqnorm(male_data$median)
qqline(male_data$median, col = "red")

qqnorm(female_data$median)
qqline(female_data$median, col = "red")

shapiro.test(male_data$median)
shapiro.test(female_data$median)
```
From the result, we can see that "median" by gender is not normally distributed. We would therefore use the Wilcoxon test to compare the mean of the data.

### Wilcoxon Test

```{r, out.width="50%", fig.align = 'center'}
wilcox.test(male_data$median, female_data$median, alt = "less")
```

This suggests that there is evidence to support a lower median frequency in the male group compared to the female group.


## meanfun

### Visualizing the data

We first visualize the data by plotting the histogram 

```{r, out.width="50%", fig.align = 'center'}
visualize_data("meanfun")
```

```{r, out.width="50%", fig.align = 'center'}
variable <- "meanfun"
boxplot(male_data[[variable]], female_data[[variable]])
```

### QQ-plot

We then plot the QQ-plot & conduct shapiro test to check for normality

```{r, out.width="50%", fig.align = 'center'}
qqnorm(male_data$meanfun)
qqline(male_data$meanfun, col = "red")

qqnorm(female_data$meanfun)
qqline(female_data$meanfun, col = "red")

shapiro.test(male_data$meanfun)
shapiro.test(female_data$meanfun)
```

From the result, we can see that "meanfun" by gender is not normally distributed. We would therefore use the Wilcoxon test to compare the mean of the data.

### Wilcoxon Test

```{r, out.width="50%", fig.align = 'center'}
wilcox.test(male_data$meanfun, female_data$meanfun, alt = "less")
```

This suggests that there is evidence to support a lower mean fundamental frequency in the male group compared to the female group.

## sd

### Visualizing the data

We first visualize the data by plotting the histogram 

```{r, out.width="50%", fig.align = 'center'}
visualize_data("sd")
```

```{r, out.width="50%", fig.align = 'center'}
variable <- "sd"
boxplot(male_data[[variable]], female_data[[variable]])
```

### QQ-plot

We then plot the QQ-plot & conduct shapiro test to check for normality

```{r, out.width="50%", fig.align = 'center'}
qqnorm(male_data$sd)
qqline(male_data$sd, col = "red")

qqnorm(female_data$sd)
qqline(female_data$sd, col = "red")

shapiro.test(male_data$sd)
shapiro.test(female_data$sd)
```
From the result, we can see that "sd" by gender is not normally distributed. We would therefore use the Wilcoxon test to compare the mean of the data.

### Wilcoxon Test

```{r, out.width="50%", fig.align = 'center'}
wilcox.test(male_data$sd, female_data$sd, alt = "greater")
```

This suggests that there is evidence to support a higher standard deviation in the male group compared to the female group.

## skew

### Visualizing the data

We first visualize the data by plotting the histogram 

```{r, out.width="50%", fig.align = 'center'}
visualize_data("skew")
```

```{r, out.width="50%", fig.align = 'center'}
variable <- "skew"
boxplot(male_data[[variable]], female_data[[variable]])
```

### QQ-plot

We then plot the QQ-plot & conduct shapiro test to check for normality

```{r, out.width="50%", fig.align = 'center'}
qqnorm(male_data$skew)
qqline(male_data$skew, col = "red")

qqnorm(female_data$skew)
qqline(female_data$skew, col = "red")

shapiro.test(male_data$skew)
shapiro.test(female_data$skew)
```

From the result, we can see that "skew" by gender is not normally distributed. We would therefore use the Wilcoxon test to compare the mean of the data.

### Wilcoxon Test

```{r, out.width="50%", fig.align = 'center'}
wilcox.test(male_data$skew, female_data$skew, alt = "two.sided")
```

This suggests that there is evidence to support a significant difference of skewness in the male group compared to the female group.

## sp.ent

### Visualizing the data

We first visualize the data by plotting the histogram 

```{r, out.width="50%", fig.align = 'center'}
visualize_data("sp.ent")
```

```{r, out.width="50%", fig.align = 'center'}
variable <- "sp.ent"
boxplot(male_data[[variable]], female_data[[variable]])
```

### QQ-plot

We then plot the QQ-plot & conduct shapiro test to check for normality

```{r, out.width="50%", fig.align = 'center'}
qqnorm(male_data$sp.ent)
qqline(male_data$sp.ent, col = "red")

qqnorm(female_data$sp.ent)
qqline(female_data$sp.ent, col = "red")

shapiro.test(male_data$sp.ent)
shapiro.test(female_data$sp.ent)
```

From the result, we can see that "sp.ent" by gender is not normally distributed. We would therefore use the Wilcoxon test to compare the mean of the data.

### Wilcoxon Test

```{r, out.width="50%", fig.align = 'center'}
wilcox.test(male_data$sp.ent, female_data$sp.ent, alt = "greater")
```

This suggests that there is evidence to support a higher specetral entropy in the male group compared to the female group.

## sfm

### Visualizing the data

We first visualize the data by plotting the histogram 

```{r, out.width="50%", fig.align = 'center'}
visualize_data("sfm")
```

```{r, out.width="50%", fig.align = 'center'}
variable <- "sfm"
boxplot(male_data[[variable]], female_data[[variable]])
```

### QQ-plot

We then plot the QQ-plot & conduct shapiro test to check for normality

```{r, out.width="50%", fig.align = 'center'}
qqnorm(male_data$sfm)
qqline(male_data$sfm, col = "red")

qqnorm(female_data$sfm)
qqline(female_data$sfm, col = "red")

shapiro.test(male_data$sfm)
shapiro.test(female_data$sfm)
```

From the result, we can see that "sfm" by gender is not normally distributed. We would therefore use the Wilcoxon test to compare the mean of the data.

### Wilcoxon Test

```{r, out.width="50%", fig.align = 'center'}
wilcox.test(male_data$sfm, female_data$sfm, alt = "two.sided")
```

This suggests that there is NO evidence to support a different sfm in the male group compared to the female group.
