---
title: "Analysis"
knit: (function(inputFile, encoding) {
      out_dir <- "../docs/age";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
output:
  html_document:
    theme: journal
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
MALE_COLOR = rgb(0, 0, 1, 0.2)
FEMALE_COLOR = rgb(1, 0, 0, 0.2)
```

# Data Preparation

```{r}
voice = read.csv("../../data/original/train.csv")
voice = voice[voice$age != "nan", ]
voice = voice[voice$gender == "male", ]
AGE_LEVELS = c("teens", "twenties", "thirties", "fourties", "fifties", "sixties", "seventies")
voice$age <- factor(voice$age, levels = AGE_LEVELS)
head(voice)
```

```{r}
check_normality <- function(column) {
  for (age in AGE_LEVELS) {
    data_age = voice[voice$age == age, ]
    data_age = data_age[[column]]
    result = shapiro.test(data_age)$p.value
    print(paste("Shapiro-Wilk test for", age, ":", result))
  }
}
```


# Data Analysis


## Mean Frequency

### Visualizing the data

```{r}
library(ggplot2)

ggplot(voice, aes(x = age, y = meanfreq, fill = age)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Pastel1") +
  labs(title = "Mean Frequency by Age Group", x = "Age Group", y = "Mean Frequency") +
  theme_minimal()
```

### Check for normality

```{r}
check_normality("meanfreq")
```

### Kruskal-Wallis Test

```{r}
kruskal.test(meanfreq ~ age, data = voice)
```

### Pairwise Wilcoxon Test

```{r}
pairwise.wilcox.test(voice$meanfreq, voice$age, p.adjust.method = "BH")
```
## Standard Deviation

### Visualizing the data

```{r}
library(ggplot2)

ggplot(voice, aes(x = age, y = sd, fill = age)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Pastel1") +
  labs(title = "sd by Age Group", x = "Age Group", y = "sd") +
  theme_minimal()
```

### Check for normality

```{r}
check_normality("sd")
```

### Kruskal-Wallis Test

```{r}
kruskal.test(sd ~ age, data = voice)
```

### Pairwise Wilcoxon Test

```{r}
pairwise.wilcox.test(voice$sd, voice$age, p.adjust.method = "BH")
```


## Q25

### Visualizing the data

```{r}
library(ggplot2)

ggplot(voice, aes(x = age, y = Q25, fill = age)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Pastel1") +
  labs(title = "Q25 by Age Group", x = "Age Group", y = "Q25") +
  theme_minimal()
```

### Check for normality

```{r}
check_normality("Q25")
```

### Kruskal-Wallis Test

```{r}
kruskal.test(Q25 ~ age, data = voice)
```

### Pairwise Wilcoxon Test

```{r}
pairwise.wilcox.test(voice$Q25, voice$age, p.adjust.method = "BH")
```

## Q75

### Visualizing the data

```{r}
library(ggplot2)

ggplot(voice, aes(x = age, y = Q75, fill = age)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Pastel1") +
  labs(title = "Q75 by Age Group", x = "Age Group", y = "Q75") +
  theme_minimal()
```

### Check for normality

```{r}
check_normality("Q75")
```

### Kruskal-Wallis Test

```{r}
kruskal.test(Q75 ~ age, data = voice)
```

### Pairwise Wilcoxon Test

```{r}
pairwise.wilcox.test(voice$Q75, voice$age, p.adjust.method = "BH")
```

## Skewness

### Visualizing the data

```{r}
library(ggplot2)

ggplot(voice, aes(x = age, y = skew, fill = age)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Pastel1") +
  labs(title = "Skewness by Age Group", x = "Age Group", y = "Skewness") +
  theme_minimal()
```

### Check for normality

```{r}
check_normality("skew")
```

### Kruskal-Wallis Test

```{r}
kruskal.test(skew ~ age, data = voice)
```

### Pairwise Wilcoxon Test

```{r}
pairwise.wilcox.test(voice$skew, voice$age, p.adjust.method = "BH")
```

## sp.ent

### Visualizing the data

```{r}
library(ggplot2)

ggplot(voice, aes(x = age, y = sp.ent, fill = age)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Pastel1") +
  labs(title = "sp.ent by Age Group", x = "Age Group", y = "sp.ent") +
  theme_minimal()
```

### Check for normality

```{r}
check_normality("sp.ent")
```

### Kruskal-Wallis Test

```{r}
kruskal.test(sp.ent ~ age, data = voice)
```

### Pairwise Wilcoxon Test

```{r}
pairwise.wilcox.test(voice$sp.ent, voice$age, p.adjust.method = "BH")
```

## sfm

### Visualizing the data

```{r}
library(ggplot2)

ggplot(voice, aes(x = age, y = sfm, fill = age)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Pastel1") +
  labs(title = "sfm by Age Group", x = "Age Group", y = "sfm") +
  theme_minimal()
```

### Check for normality

```{r}
check_normality("sfm")
```

### Kruskal-Wallis Test

```{r}
kruskal.test(sfm ~ age, data = voice)
```

### Pairwise Wilcoxon Test

```{r}
pairwise.wilcox.test(voice$sfm, voice$age, p.adjust.method = "BH")
```

## minfun

### Visualizing the data

```{r}
library(ggplot2)

ggplot(voice, aes(x = age, y = minfun, fill = age)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Pastel1") +
  labs(title = "minfun by Age Group", x = "Age Group", y = "minfun") +
  theme_minimal()
```

### Check for normality

```{r}
check_normality("minfun")
```

### Kruskal-Wallis Test

```{r}
kruskal.test(minfun ~ age, data = voice)
```

### Pairwise Wilcoxon Test

```{r}
pairwise.wilcox.test(voice$minfun, voice$age, p.adjust.method = "BH")
```