---
title: "Data Analysis for SD"
knit: (function(inputFile, encoding) {
      out_dir <- "../../report/graphs/";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir),
                        output_format = "pdf_document")})
output:
  pdf_document: default
---

## Load Data

```{r}
data_path <- "../../data/original/train.csv"
voice <- read.csv(data_path)
head(voice)
```

## Visualizing the Data

We selected `sd` column to perform the analysis.

First, we load the data and draw a histogram of the `sd` column to get an initial understanding of the data distribution.

```{r, out.width="50%", fig.align = 'center'}
sd <- voice$sd
hist(sd, breaks = 80, main = "Histogram of sd", xlab = "sd")
boxplot(sd, main = "Boxplot of sd")
```

Then, we generate the descriptive statistics of the `sd` column.

```{r, warning=FALSE}
library(psych)
describe(sd, type = 1)
```

## Assessing Data Normality

After that, we assess the normality of the `sd` column by drawing a histogram with a normal curve and a Q-Q plot.

```{r, out.width="50%", fig.align = 'center'}
hist(sd, breaks = 80, main = "Histogram of sd", xlab = "sd")
# impose a normal curve on the histogram
xpt <- seq(402, 4203, by = 0.1)
n_den <- dnorm(xpt, mean = mean(sd), sd = sd(sd))
ypt <- n_den * length(sd) * 50
lines(xpt, ypt, col = "red")
```

```{r, out.width="50%", fig.align = 'center'}
qqnorm(sd)
qqline(sd, col = "blue")
```

## Transformation

We found that the data is almost normally distributed, but not perfect. We tried to log-transform the data to see if it can be improved.

```{r, out.width="50%", fig.align = 'center'}
sd_trans <- log(sd)
hist(sd_trans, breaks = 80, main = "Histogram of log(sd)", xlab = "log(sd)")
```

```{r, out.width="50%", fig.align = 'center'}
qqnorm(sd_trans)
qqline(sd_trans, col = "red")
```

We observed that after log-transformation, the data's fit to a normal distribution did not improve as expected.

Therefore, we explored an alternative transformation: $y=\log(x + 3000)$

```{r, out.width="50%", fig.align = 'center'}
sd_trans <- log(sd + 3000)

hist(
  sd_trans,
  breaks = 80,
  main = "Histogram of log(sd)",
  xlab = "log(sd)",
  probability = TRUE
)

curve(
  dnorm(x, mean = mean(sd_trans), sd = sd(sd_trans)),
  col = "red",
  lwd = 2,
  add = TRUE
)
```

And we checked the Q-Q plot of the transformed data.

```{r, out.width="50%", fig.align = 'center'}
qqnorm(sd_trans)
qqline(sd_trans, col = "red")
```

Finally, we calculated the descriptive statistics of the transformed data.

```{r}
describe(sd_trans)
```
