---
title: "Data Analysis by Age on Mean Frequency"
knit: (function(inputFile, encoding) {
      out_dir <- "../../report/graphs";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir),
                        output_format = "pdf_document")})
output:
  html_document:
    theme: journal
    toc: true
    toc_float: true
---
```{r setup, include=FALSE}
MALE_COLOR <- rgb(0, 0, 1, 0.2)
FEMALE_COLOR <- rgb(1, 0, 0, 0.2)
```

# Data Preparation

```{r}
voice <- read.csv("../../data/gender/balanced_train.csv")
head(voice)
```

```{r}
male_data <- voice[voice$gender == "male", ]
female_data <- voice[voice$gender == "female", ]
head(male_data)
head(female_data)
```

### Visualizing the data

```{r}
visualize_data <- function(column) {
  # return(male_data[column])
  hist(
    male_data[[column]],
    xlab = column,
    col = MALE_COLOR,
    prob = TRUE,
    breaks = 80,
    border = "white",
    main = sprintf("Histogram and KDE of %s", column)
  )
  hist(
    female_data[[column]],
    xlab = column,
    col = FEMALE_COLOR,
    prob = TRUE,
    add = TRUE,
    breaks = 80,
    border = "white"
  )

  # Calculate and plot KDE for male data
  male_density <- density(male_data[[column]])
  lines(male_density, col = "blue", lwd = 2)

  # Calculate and plot KDE for female data
  female_density <- density(female_data[[column]])
  lines(female_density, col = "red", lwd = 2)

  legend(
    "topright",
    legend = c("Male", "Female"),
    col = c("blue", "red"),
    lwd = 2,
    fill = c(MALE_COLOR, FEMALE_COLOR)
  )
}
```


We first visualize the data by plotting the histogram.

```{r}
visualize_data("meanfreq")
```

```{r}
variable <- "meanfreq"
boxplot(male_data[[variable]], female_data[[variable]])
```

### QQ-plot

We then plot the QQ-plot to check for normality

```{r}
qqnorm(male_data$meanfreq)
qqline(male_data$meanfreq, col = "red")


qqnorm(female_data$meanfreq)
qqline(female_data$meanfreq, col = "red")

shapiro.test(male_data$meanfreq)
shapiro.test(female_data$meanfreq)
```

Based on the QQ-plot, we can see that the data is normally distributed. We would therefore use the F test to compare the variance of the data

### F-test

```{r}
var.test(male_data$meanfreq, female_data$meanfreq)
```

Since the p-value is less than 0.05, we reject the null hypothesis that the variance of the data is the same, we would therefore use the two sample t-test with unequal variance

### Two Sample T-test

```{r}
t.test(male_data$meanfreq, female_data$meanfreq, var.equal = FALSE)
```

Since the p-value is greater than 0.05, we do not reject the null hypothesis that the mean of the data is the same.
