---
title: "Data Analysis"
knit: (function(inputFile, encoding) {
      out_dir <- "../docs/";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir));
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir),
                        output_format = "pdf_document")})
output:
  html_document:
    theme: journal
    toc: true
    toc_float: true
  pdf_document: default
---

# Load Data

```{r}
data_path <- "../data/original/train.csv"
voice <- read.csv(data_path)
head(voice)
```

# Analyze Data

## MeanFreq

### Basic Analysis

We firstly load the data and draw a histogram of the `meanfreq` column.

```{r}
meanfreq <- voice$meanfreq
hist(meanfreq)
```

Then, we calculate the mean and standard deviation of the `meanfreq` column.

```{r}
# hist of meanfreq
hist(meanfreq, breaks = 80, main = "Histogram of meanfreq", xlab = "meanfreq")
# impose a normal curve on the histogram
xpt <- seq(698, 7056, by = 0.1)
n_den <- dnorm(xpt, mean = mean(meanfreq), sd = sd(meanfreq))
ypt <- n_den * length(meanfreq) * 100
lines(xpt, ypt, col = "red")
```

#### QQ plot for meanfreq

```{r}
# QQplot of meanfreq
qqnorm(meanfreq)
qqline(meanfreq, col = "blue")
title("QQplot for meanfreq", line = 1) # Place title on the first line
```

#### shapiro test

Shapiro test-sample must be less than 5000. Therefore, we will take a sample of 5000 for 100 times

```{r}
pvalue <- numeric(100)
for (i in 1:100) {
  meanfreq_sample <- sample(meanfreq, 5000)
  shapiro.test(meanfreq_sample)
  pvalue[i] <- shapiro.test(meanfreq_sample)$p.value
}
pvalue > 0.05
```

Therefore, the data is not normally distributed.

### log-transformation

```{r}
meanfreq_trans <- log(meanfreq)
hist(
  meanfreq_trans,
  breaks = 80,
  main = "Histogram of log(meanfreq)",
  xlab = "log(meanfreq)"
)
range(meanfreq_trans)
# impose a normal curve on the histogram
xpt <- seq(6, 9, by = 0.1)
n_den <- dnorm(xpt, mean = mean(meanfreq_trans), sd = sd(meanfreq_trans))
ypt <- n_den * length(meanfreq_trans) * 0.05
lines(xpt, ypt, col = "red")
```

#### QQ plot for Transformed meanfreq

```{r}
qqnorm(meanfreq_trans)
qqline(meanfreq_trans, col = "red")
title("QQplot for meanfreq-log") # Place title on the first line
```

## SD

### Basic Analysis

We firstly load the data and draw a histogram of the `sd` column.

```{r}
sd <- voice$sd
hist(sd)
```

```{r}
hist(sd, breaks = 80, main = "Histogram of sd", xlab = "sd")
# impose a normal curve on the histogram
xpt <- seq(402, 4203, by = 0.1)
n_den <- dnorm(xpt, mean = mean(sd), sd = sd(sd))
ypt <- n_den * length(sd) * 50
lines(xpt, ypt, col = "red")
```

```{r}
qqnorm(sd)
qqline(sd, col = "blue")
```


### log-transformation

```{r}
# log-transformation of sd
sd_trans <- log(sd)
hist(sd_trans, breaks = 80, main = "Histogram of log(sd)", xlab = "log(sd)")
```

```{r}
qqnorm(sd_trans)
qqline(sd_trans, col = "red")
```

We found that after log-transformation, the data is even worse than before. 

Therefore, we tried another way: $y=\log(x + 3000)$

```{r}
sd_trans <- log(sd + 3000)
hist(sd_trans, breaks = 80, main = "Histogram of log(sd)", xlab = "log(sd)")
```

```{r}
hist(
  sd_trans,
  breaks = 80,
  main = "Histogram of log(sd)",
  xlab = "log(sd)",
  probability = TRUE
)
curve(
  dnorm(x, mean = mean(sd_trans), sd = sd(sd_trans)),
  col = "red",
  lwd = 2,
  add = TRUE
)
```


```{r}
qqnorm(sd_trans)
qqline(sd_trans, col = "red")
```

## Median

### Basic Analysis

We firstly load the data and draw a histogram of the `median` column.

```{r}
median <- voice$median
hist(median, breaks = 80, main = "Histogram of median", xlab = "median")
```

Then, we calculate the mean and standard deviation of the `median` column.

```{r}
median_mean <- mean(median)
median_sd <- sd(median)
```

```{r}
hist(median, breaks = 80, main = "Histogram of median", xlab = "median", probability = TRUE)
curve(
  dnorm(x, mean = median_mean, sd = median_sd),
  col = "red",
  lwd = 2,
  add = TRUE
)
```

```{r}
qqnorm(median)
qqline(median, col = "blue")
```

### log-transformation

```{r}
median_trans <- log(median + 0.01)
hist(median_trans, breaks = 80, main = "Histogram of log(median)", xlab = "log(median)")
```

```{r}
hist(
  median_trans,
  breaks = 90,
  main = "Histogram of log(median)",
  xlab = "log(median)",
  probability = TRUE
)
curve(
  dnorm(x, mean = mean(median_trans), sd = sd(median_trans)),
  col = "red", lwd = 2,
  add = TRUE
)
```

```{r}
qqnorm(median_trans)
qqline(median_trans, col = "red")
```

## Q25

### Basic Analysis

We firstly load the data and draw a histogram of the `Q25` column.

```{r}
Q25 <- voice$Q25
hist(Q25, breaks = 80, main = "Histogram of Q25", xlab = "Q25")
```

Then, we calculate the mean and standard deviation of the `Q25` column.

```{r}
Q25_mean <- mean(Q25)
Q25_sd <- sd(Q25)
```

```{r}
hist(Q25, breaks = 80, main = "Histogram of Q25", xlab = "Q25", probability = TRUE)
curve(dnorm(x, mean = Q25_mean, sd = Q25_sd), col = "red", lwd = 2, add = TRUE)
```

#### QQ plot for Q25

```{r}
qqnorm(Q25)
qqline(Q25, col = "blue")
```

### log-transformation

After multiple attempts to transform the `Q25` column, we found that the log-transformation with $f(x)=\log(x - \min(x) + 70)$ is the best transformation for this column.


```{r}
Q25_trans <- log(Q25 + 70)
hist(Q25_trans, breaks = 80, main = "Histogram of log(Q25)", xlab = "log(Q25)")
```

```{r}
hist(Q25_trans, breaks = 80, main = "Histogram of log(Q25)", xlab = "log(Q25)", probability = TRUE)
curve(dnorm(x, mean = mean(Q25_trans), sd = sd(Q25_trans)), col = "red", lwd = 2, add = TRUE)
```


```{r}
qqnorm(Q25_trans)
qqline(Q25_trans, col = "red")
```

## Q75

### Basic Analysis

We firstly load the data and draw a histogram of the `Q75` column.

```{r}
Q75 <- voice$Q75
hist(Q75)
```

Then, we calculate the mean and standard deviation of the `Q75` column.

```{r}
Q75_mean <- mean(Q75)
Q75_sd <- sd(Q75)
print(paste("Mean of Q75:", Q75_mean))
print(paste("Standard deviation of Q75:", Q75_sd))
```

#### Histogram with overlaid normal curve

```{r}
hist(Q75, probability = TRUE, main = "Histogram of Q75 with Normal Curve", xlab = "Q75")
curve(dnorm(x, mean = Q75_mean, sd = Q75_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

#### QQ plot

```{r}
qqnorm(Q75, main = "QQ Plot of Q75")
qqline(Q75, col = "steelblue", lwd = 2)
```

### Transformed `Q75`

```{r}
Q75_trans <- log(Q75 + 5000)
hist(Q75_trans, breaks = 20, main = "Histogram of log(Q75)", xlab = "log(Q75)")
Q75_trans_mean <- mean(Q75_trans)
Q75_trans_sd <- sd(Q75_trans)
print(paste("Mean of Transformed Q75:", Q75_trans_mean))
print(paste("Standard deviation of Transformed Q75:", Q75_trans_sd))
```

#### Histogram with overlaid normal curve

```{r}
hist(Q75_trans, probability = TRUE, main = "Histogram of Transformed Q75 with Normal Curve", xlab = "log(Q75)")
curve(dnorm(x, mean = Q75_trans_mean, sd = Q75_trans_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

#### QQ plot for Transformed `Q75`

```{r}
qqnorm(Q75_trans, main = "QQ Plot for Transformed Q75")
qqline(Q75_trans, col = "red")
```


## IQR

### Basic Analysis

```{r}
IQR <- voice$IQR
hist(IQR)
```

Then, we calculate the mean and standard deviation of the `IQR` column.

```{r}
IQR_mean <- mean(IQR)
IQR_sd <- sd(IQR)
```

The `IQR` column is almost normally distributed, we can see that from the histogram and QQ plot below.

```{r}
hist(IQR, probability = TRUE, main = "Histogram of IQR with Normal Curve", xlab = "IQR", breaks = 20)
curve(dnorm(x, mean = IQR_mean, sd = IQR_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(IQR, main = "QQ Plot of IQR")
qqline(IQR, col = "steelblue", lwd = 2)
```

## skew

### Basic Analysis

```{r}
skew <- voice$skew
hist(skew, breaks = 80, main = "Histogram of skew", xlab = "skew")
```

Then, we calculate the mean and standard deviation of the `skew` column.

```{r}
skew_mean <- mean(skew)
skew_sd <- sd(skew)
```

The `skew` column is almost normally distributed, we can see that from the histogram and QQ plot below.

```{r}
hist(skew, probability = TRUE, main = "Histogram of skew with Normal Curve", xlab = "IQR", breaks = 80)
curve(dnorm(x, mean = skew_mean, sd = skew_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(skew, main = "QQ Plot of skew")
qqline(skew, col = "steelblue", lwd = 2)
```

## kurt

```{r}
kurt <- voice$kurt
hist(kurt, breaks = 80, main = "Histogram of kurt", xlab = "kurt")
```

Then, we calculate the mean and standard deviation of the `kurt` column.

```{r}
kurt_mean <- mean(kurt)
kurt_sd <- sd(kurt)
```

The `kurt` column is almost normally distributed, we can see that from the histogram and QQ plot below.

```{r}
hist(kurt, probability = TRUE, main = "Histogram of kurt with Normal Curve", xlab = "kurt", breaks = 80)
curve(dnorm(x, mean = kurt_mean, sd = kurt_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(kurt, main = "QQ Plot of kurt")
qqline(kurt, col = "steelblue", lwd = 2)
```

### Transformed `kurt`

```{r}
kurt_trans <- log(kurt + 0.31)
hist(kurt_trans, breaks = 80, main = "Histogram of log(kurt)", xlab = "log(kurt)")
kurt_trans_mean <- mean(kurt_trans)
kurt_trans_sd <- sd(kurt_trans)
print(paste("Mean of Transformed kurt:", kurt_trans_mean))
print(paste("Standard deviation of Transformed kurt:", kurt_trans_sd))
```

#### Histogram with overlaid normal curve

```{r}
hist(kurt_trans, probability = TRUE, main = "Histogram of Transformed Kurt with Normal Curve", xlab = "log(kurt)", breaks = 80)
curve(dnorm(x, mean = kurt_trans_mean, sd = kurt_trans_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

#### QQ plot for Transformed `kurt`

```{r}
qqnorm(kurt_trans, main = "QQ Plot for Transformed kurt")
qqline(kurt_trans, col = "red")
```

## sp.ent

### Basic Analysis

```{r}
sp_ent <- voice$sp.ent
hist(sp_ent, breaks = 80, main = "Histogram of sp.ent", xlab = "sp.ent")
```

Then, we calculate the mean and standard deviation of the `sp.ent` column.

```{r}
sp_ent_mean <- mean(sp_ent)
sp_ent_sd <- sd(sp_ent)
print(paste("Mean of sp.ent:", sp_ent_mean))
print(paste("Standard deviation of sp.ent:", sp_ent_sd))
```


```{r}
hist(sp_ent, probability = TRUE, main = "Histogram of sp.ent with Normal Curve", xlab = "sp.ent", breaks = 80)
curve(dnorm(x, mean = sp_ent_mean, sd = sp_ent_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(sp_ent, main = "QQ Plot of sp.ent")
qqline(sp_ent, col = "steelblue", lwd = 2)
```
### Transformed `sp.ent`

```{r}
sp_ent_trans <- sqrt(log(sp_ent) + 10)
hist(sp_ent_trans, breaks = 80, main = "Histogram of log(sp.ent)", xlab = "log(sp.ent)")
```

```{r}
sp_ent_trans_mean <- mean(sp_ent_trans)
sp_ent_trans_sd <- sd(sp_ent_trans)
print(paste("Mean of Transformed sp.ent:", sp_ent_trans_mean))
print(paste("Standard deviation of Transformed sp.ent:", sp_ent_trans_sd))
```

```{r}
hist(sp_ent_trans, probability = TRUE, main = "Histogram of Transformed sp.ent with Normal Curve", xlab = "log(sp.ent)", breaks = 80)
curve(dnorm(x, mean = sp_ent_trans_mean, sd = sp_ent_trans_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(sp_ent_trans, main = "QQ Plot for Transformed sp.ent")
qqline(sp_ent_trans, col = "red")
```

## sfm

### Basic Analysis

```{r}
sfm <- voice$sfm
hist(sfm, breaks = 80, main = "Histogram of sfm", xlab = "sfm")
```

Then, we calculate the mean and standard deviation of the `sfm` column.

```{r}
sfm_mean <- mean(sfm)
sfm_sd <- sd(sfm)
print(paste("Mean of sfm:", sfm_mean))
print(paste("Standard deviation of sfm:", sfm_sd))
```

```{r}
hist(sfm, probability = TRUE, main = "Histogram of sfm with Normal Curve", xlab = "sfm", breaks = 80)
curve(dnorm(x, mean = sfm_mean, sd = sfm_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(sfm, main = "QQ Plot of sfm")
qqline(sfm, col = "steelblue", lwd = 2)
```

### Transformed `sfm`

```{r}
sfm_trans <- sqrt(log(sfm) + 10)
hist(sfm_trans, breaks = 80, main = "Histogram of log(sfm)", xlab = "log(sfm)")
```

```{r}
sfm_trans_mean <- mean(sfm_trans)
sfm_trans_sd <- sd(sfm_trans)
print(paste("Mean of Transformed sfm:", sfm_trans_mean))
print(paste("Standard deviation of Transformed sfm:", sfm_trans_sd))
```

```{r}
hist(sfm_trans, probability = TRUE, main = "Histogram of Transformed sfm with Normal Curve", xlab = "log(sfm)", breaks = 80)
curve(dnorm(x, mean = sfm_trans_mean, sd = sfm_trans_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(sfm_trans, main = "QQ Plot for Transformed sfm")
qqline(sfm_trans, col = "red")
```

## mode

### Basic Analysis

```{r}
mode <- voice$mode
hist(mode, breaks = 80, main = "Histogram of mode", xlab = "mode")
```

Then, we calculate the mean and standard deviation of the `mode` column.

```{r}
mode_mean <- mean(mode)
mode_sd <- sd(mode)
print(paste("Mean of mode:", mode_mean))
print(paste("Standard deviation of mode:", mode_sd))
```

```{r}
hist(mode, probability = TRUE, main = "Histogram of mode with Normal Curve", xlab = "mode", breaks = 80)
curve(dnorm(x, mean = mode_mean, sd = mode_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(mode, main = "QQ Plot of mode")
qqline(mode, col = "steelblue", lwd = 2)
```

### Transformed `mode`

```{r}
mode_trans <- log(mode + 100)
hist(mode_trans, breaks = 80, main = "Histogram of log(mode)", xlab = "log(mode)")
```

```{r}
mode_trans_mean <- mean(mode_trans)
mode_trans_sd <- sd(mode_trans)
print(paste("Mean of Transformed mode:", mode_trans_mean))
print(paste("Standard deviation of Transformed mode:", mode_trans_sd))
```

```{r}
hist(mode_trans, probability = TRUE, main = "Histogram of Transformed mode with Normal Curve", xlab = "log(mode)", breaks = 80)
curve(dnorm(x, mean = mode_trans_mean, sd = mode_trans_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(mode_trans, main = "QQ Plot for Transformed mode")
qqline(mode_trans, col = "red")
```

## Centroid

### Basic Analysis

We firstly load the data and draw a histogram of the `centroid` column.

```{r}
centroid <- voice$centroid
hist(centroid, breaks = 80, main = "Histogram of centroid", xlab = "centroid")
```

Then, we calculate the mean and standard deviation of the `centroid` column.

```{r}
centroid_mean <- mean(centroid)
centroid_sd <- sd(centroid)
print(paste("Mean of centroid:", centroid_mean))
print(paste("Standard deviation of centroid:", centroid_sd))
```

#### Histogram with overlaid normal curve

```{r}
hist(centroid, probability = TRUE, main = "Histogram of Centroid with Normal Curve", xlab = "Centroid", breaks = 80)
curve(dnorm(x, mean = centroid_mean, sd = centroid_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

#### QQ plot

```{r}
qqnorm(centroid, main = "QQ Plot of Centroid")
qqline(centroid, col = "steelblue", lwd = 2)
```

### Transformed `centroid`

```{r}
centroid_trans <- log(centroid)
hist(centroid_trans, breaks = 80, main = "Histogram of log(centroid)", xlab = "log(centroid)")
centroid_trans_mean <- mean(centroid_trans)
centroid_trans_sd <- sd(centroid_trans)
print(paste("Mean of Transformed centroid:", centroid_trans_mean))
print(paste("Standard deviation of Transformed centroid:", centroid_trans_sd))
```

#### Histogram with overlaid normal curve

```{r}
hist(centroid_trans, probability = TRUE, main = "Histogram of Transformed Centroid with Normal Curve", xlab = "log(centroid)", breaks = 80)
curve(dnorm(x, mean = centroid_trans_mean, sd = centroid_trans_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

#### QQ plot for Transformed `centroid`

```{r}
qqnorm(centroid_trans, main = "QQ Plot for Transformed centroid")
qqline(centroid_trans, col = "red")
```

## MeanFun

### Basic Analysis

```{r}
meanfun <- voice$meanfun
hist(meanfun)
```

Then, we calculate the mean and standard deviation of the `meanfun` column.

```{r}
meanfun_mean <- mean(meanfun)
meanfun_sd <- sd(meanfun)
```

It is very obvious that the `meanfun` column is not normally distributed, we can see that from the histogram and QQ plot below.

```{r}
hist(meanfun, probability = TRUE, main = "Histogram of MeanFun with Normal Curve", xlab = "MeanFun", breaks = 80)
curve(dnorm(x, mean = meanfun_mean, sd = meanfun_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(meanfun, main = "QQ Plot of MeanFun")
qqline(meanfun, col = "steelblue", lwd = 2)
```

### Transformed `meanfun`

```{r}
meanfun_trans <- log(meanfun + 3)
hist(meanfun_trans, breaks = 80, main = "Histogram of log(meanfun)", xlab = "log(meanfun)")
```

```{r}
meanfun_trans_mean <- mean(meanfun_trans)
meanfun_trans_sd <- sd(meanfun_trans)
print(paste("Mean of Transformed meanfun:", meanfun_trans_mean))
print(paste("Standard deviation of Transformed meanfun:", meanfun_trans_sd))
```

```{r}
hist(meanfun_trans, probability = TRUE, main = "Histogram of Transformed MeanFun with Normal Curve", xlab = "log(meanfun)", breaks = 80)
curve(dnorm(x, mean = meanfun_trans_mean, sd = meanfun_trans_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(meanfun_trans, main = "QQ Plot for Transformed meanfun")
qqline(meanfun_trans, col = "red")
```

## MinFun

### Basic Analysis

```{r}
minfun <- voice$minfun
hist(minfun, breaks = 80, main = "Histogram of minfun", xlab = "minfun")
```

Then, we calculate the mean and standard deviation of the `minfun` column.

```{r}
minfun_mean <- mean(minfun)
minfun_sd <- sd(minfun)
print(paste("Mean of minfun:", minfun_mean))
print(paste("Standard deviation of minfun:", minfun_sd))
```

```{r}
hist(minfun, probability = TRUE, main = "Histogram of MinFun with Normal Curve", xlab = "MinFun", breaks = 80)
curve(dnorm(x, mean = minfun_mean, sd = minfun_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(minfun, main = "QQ Plot of MinFun")
qqline(minfun, col = "steelblue", lwd = 2)
```

### Transformed `minfun`

```{r}
min(minfun)
```


```{r}
minfun_trans <- log(10 * log(minfun - 151.35) + 0.7)
hist(minfun_trans, breaks = 80, main = "Histogram of log(minfun)", xlab = "log(minfun)")
```

```{r}
hist(minfun_trans, probability = TRUE, main = "Histogram of Transformed MinFun with Normal Curve", xlab = "log(minfun)", breaks = 80)
curve(dnorm(x, mean = mean(minfun_trans), sd = sd(minfun_trans)), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```


```{r}
qqnorm(minfun_trans)
qqline(minfun_trans, col = "blue")
```

## MaxFun

### Basic Analysis

```{r}
maxfun <- voice$maxfun
hist(maxfun, breaks = 80, main = "Histogram of maxfun", xlab = "maxfun")
```

Then, we calculate the mean and standard deviation of the `maxfun` column.

```{r}
maxfun_mean <- mean(maxfun)
maxfun_sd <- sd(maxfun)
print(paste("Mean of maxfun:", maxfun_mean))
print(paste("Standard deviation of maxfun:", maxfun_sd))
```

```{r}
hist(maxfun, probability = TRUE, main = "Histogram of MaxFun with Normal Curve", xlab = "MaxFun", breaks = 80)
curve(dnorm(x, mean = maxfun_mean, sd = maxfun_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

## MeanDom

### Basic Analysis
 
```{r}
meandom <- voice$meandom
hist(meandom, breaks = 80, main = "Histogram of meandom", xlab = "meandom")
```

Then, we calculate the mean and standard deviation of the `meandom` column.

```{r}
meandom_mean <- mean(meandom)
meandom_sd <- sd(meandom)
```

We then draw the histogram and QQ plot for the `meandom` column to know more about its distribution.

```{r}
hist(meandom, probability = TRUE, main = "Histogram of MeanDom with Normal Curve", xlab = "MeanDom", breaks = 80)
curve(dnorm(x, mean = meandom_mean, sd = meandom_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(meandom, main = "QQ Plot of MeanDom")
qqline(meandom, col = "steelblue", lwd = 2)
```

### Transformed `meandom`

After multiple attempts to transform the `meandom` column, we found that the log-transformation with $f(x)=\log(x + 0.01)$ is the best transformation for this column.

```{r}
meandom_trans <- log(meandom + 0.01)
hist(meandom_trans, breaks = as.integer(sqrt(length(meandom_trans))), main = "Histogram of log(meandom)", xlab = "log(meandom)")
```

```{r}
meandom_trans_mean <- mean(meandom_trans)
meandom_trans_sd <- sd(meandom_trans)
print(paste("Mean of Transformed meandom:", meandom_trans_mean))
print(paste("Standard deviation of Transformed meandom:", meandom_trans_sd))
```

```{r}
hist(meandom_trans, probability = TRUE, main = "Histogram of Transformed MeanDom with Normal Curve", xlab = "log(meandom)", breaks = as.integer(sqrt(length(meandom_trans))))
curve(dnorm(x, mean = meandom_trans_mean, sd = meandom_trans_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(meandom_trans, main = "QQ Plot for Transformed meandom")
qqline(meandom_trans, col = "red")
```

## MinDom

### Basic Analysis

```{r}
mindom <- voice$mindom
hist(mindom, breaks = 80, main = "Histogram of mindom", xlab = "mindom")
```

Then, we calculate the mean and standard deviation of the `mindom` column.

```{r}
mindom_mean <- mean(mindom)
mindom_sd <- sd(mindom)
```

We then draw the histogram and QQ plot for the `mindom` column to know more about its distribution.

```{r}
hist(mindom, probability = TRUE, main = "Histogram of MinDom with Normal Curve", xlab = "MinDom", breaks = 80)
curve(dnorm(x, mean = mindom_mean, sd = mindom_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(mindom, main = "QQ Plot of MinDom")
qqline(mindom, col = "steelblue", lwd = 2)
```

### Transformed `mindom`

```{r}
mindom_trans <- log(mindom)
hist(mindom_trans, breaks = as.integer(sqrt(length(mindom_trans))), main = "Histogram of log(mindom)", xlab = "log(mindom)")
```

```{r}
mindom_trans_mean <- mean(mindom_trans)
mindom_trans_sd <- sd(mindom_trans)
print(paste("Mean of Transformed mindom:", mindom_trans_mean))
print(paste("Standard deviation of Transformed mindom:", mindom_trans_sd))
```

```{r}
hist(mindom_trans, probability = TRUE, main = "Histogram of Transformed MinDom with Normal Curve", xlab = "log(mindom)", breaks = as.integer(sqrt(length(mindom_trans))))
curve(dnorm(x, mean = mindom_trans_mean, sd = mindom_trans_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(mindom_trans, main = "QQ Plot for Transformed mindom")
qqline(mindom_trans, col = "red")
```

## MaxDom

### Basic Analysis

```{r}
maxdom <- voice$maxdom
hist(maxdom, breaks = 80, main = "Histogram of maxdom", xlab = "maxdom")
```

Then, we calculate the mean and standard deviation of the `maxdom` column.

```{r}
maxdom_mean <- mean(maxdom)
maxdom_sd <- sd(maxdom)
```

We then draw the histogram and QQ plot for the `maxdom` column to know more about its distribution.

```{r}
hist(maxdom, probability = TRUE, main = "Histogram of MaxDom with Normal Curve", xlab = "MaxDom", breaks = 80)
curve(dnorm(x, mean = maxdom_mean, sd = maxdom_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(maxdom, main = "QQ Plot of MaxDom")
qqline(maxdom, col = "steelblue", lwd = 2)
```

### Transformed `maxdom`

```{r}
maxdom_trans <- maxdom^(1 / 3)
hist(maxdom_trans, breaks = as.integer(sqrt(length(maxdom_trans))), main = "Histogram of maxdom_trans", xlab = "maxdom_trans")
```

```{r}
hist(maxdom_trans, probability = TRUE, main = "Histogram of Transformed MaxDom with Normal Curve", xlab = "Transformed MaxDom", breaks = 80)
curve(dnorm(x, mean = mean(maxdom_trans), sd = sd(maxdom_trans)), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(maxdom_trans)
qqline(maxdom_trans, col = "red")
```

## dfrange

### Basic Analysis

```{r}
dfrange <- voice$dfrange
hist(dfrange, breaks = 80, main = "Histogram of dfrange", xlab = "dfrange")
```

Then, we calculate the mean and standard deviation of the `dfrange` column.

```{r}
dfrange_mean <- mean(dfrange)
dfrange_sd <- sd(dfrange)
```

We then draw the histogram and QQ plot for the `dfrange` column to know more about its distribution.

```{r}
hist(dfrange, probability = TRUE, main = "Histogram of dfrange with Normal Curve", xlab = "dfrange", breaks = 80)
curve(dnorm(x, mean = dfrange_mean, sd = dfrange_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(dfrange, main = "QQ Plot of dfrange")
qqline(dfrange, col = "steelblue", lwd = 2)
```

### Transformed `dfrange`

```{r}
dfrange_trans <- dfrange^(1 / 3)
hist(dfrange_trans, breaks = 80, main = "Histogram of log(dfrange)", xlab = "log(dfrange)")
```

```{r}
dfrange_trans_mean <- mean(dfrange_trans)
dfrange_trans_sd <- sd(dfrange_trans)
print(paste("Mean of Transformed dfrange:", dfrange_trans_mean))
print(paste("Standard deviation of Transformed dfrange:", dfrange_trans_sd))
```

```{r}
hist(dfrange_trans, probability = TRUE, main = "Histogram of Transformed dfrange with Normal Curve", xlab = "log(dfrange)", breaks = 80)
curve(dnorm(x, mean = dfrange_trans_mean, sd = dfrange_trans_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(dfrange_trans, main = "QQ Plot for Transformed dfrange")
qqline(dfrange_trans, col = "red")
```

## modindx

### Basic Analysis

```{r}
modindx <- voice$modindx
hist(modindx, breaks = 80, main = "Histogram of modindx", xlab = "modindx")
```

Then, we calculate the mean and standard deviation of the `modindx` column.

```{r}
modindx_mean <- mean(modindx)
modindx_sd <- sd(modindx)
print(paste("Mean of modindx:", modindx_mean))
print(paste("Standard deviation of modindx:", modindx_sd))
```

We then draw the histogram and QQ plot for the `modindx` column to know more about its distribution.

```{r}
hist(modindx, probability = TRUE, main = "Histogram of Modindx with Normal Curve", xlab = "Modindx", breaks = 80)
curve(dnorm(x, mean = modindx_mean, sd = modindx_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(modindx, main = "QQ Plot of Modindx")
qqline(modindx, col = "steelblue", lwd = 2)
```

### Transformed `modindx`

```{r}
modindx_trans <- (modindx) ^ (1 / 3)
hist(modindx_trans, breaks = 80, main = "Histogram of log(modindx)", xlab = "log(modindx)")
```


```{r}
hist(modindx_trans, breaks = 80, main = "Histogram of log(modindx)", xlab = "log(modindx)", probability = TRUE)
curve(dnorm(x, mean=mean(modindx_trans), sd=sd(modindx_trans)), col = "red", lwd = 2, add = TRUE)
```

```{r}
qqnorm(modindx)
qqline(modindx, col = "red")
```

## Age

```{r}
age <- voice$age
age_table <- table(age)
pie(age_table, main = "Pie Chart of Age Distribution")
```

```{r}
barplot(table(factor(age, levels = c("teens", "twenties", "thirties", "fourties", "fifties", "sixties", "seventies", "nan"))), main = "Bar Plot of Age Distribution", xlab = "Age", ylab = "Frequency")
```

## Gender

```{r}
gender <- voice$gender
pie(table(gender), main = "Pie Chart of Gender Distribution")
```

## Accent

```{r}
library(ggplot2)

ggplot(voice, aes(x = reorder(accent, -table(accent)[accent]), y = after_stat(count))) +
  geom_bar(stat = "count") +
  coord_flip() +
  labs(x = "Accent", y = "Count", title = "Accent Distribution") +
  theme_minimal() +
  theme(axis.text.y = element_text(hjust = 1))
```


# Merge Data

```{r}
transformed_voice <- data.frame(
  id = voice$id,
  meanfreq = meanfreq_trans,
  sd = sd_trans,
  median = median_trans,
  Q25 = Q25_trans,
  Q75 = Q75_trans,
  IQR = IQR,
  skew = skew,
  kurt = kurt_trans,
  sp.ent = sp_ent_trans,
  sfm = sfm_trans,
  mode = mode_trans,
  centroid = centroid_trans,
  meanfun = meanfun_trans,
  minfun = minfun_trans,
  maxfun = maxfun,
  meandom = meandom_trans,
  mindom = mindom_trans,
  maxdom = maxdom_trans,
  dfrange = dfrange_trans,
  modindx = modindx_trans,
  age = age,
  gender = gender,
  accent = voice$accent
)
```

```{r}
head(transformed_voice)
```

```{r}
write.csv(transformed_voice, "../data/transformated/train.csv", row.names = FALSE)
```

### Visualize the Data Before and After Transformation

```{r}
QQ_PLOT_MAX_POINTS <- 100

visualize_hist <- function(data, header, hist_color, curve_color) {
  hist(data, breaks = 80, main = header, probability = TRUE, col = hist_color, ylab = "Density", border = "white")
  data_mean <- mean(data)
  data_sd <- sd(data)
  curve(dnorm(x, mean = data_mean, sd = data_sd), col = curve_color, lwd = 2, add = TRUE, yaxt = "n")
}

visualize_qq_plot <- function(data, header, points_color, line_color) {
  if (length(data) > QQ_PLOT_MAX_POINTS) {
    data <- sample(data, QQ_PLOT_MAX_POINTS)
  }
  qqnorm(data, main = header, col = points_color)
  qqline(data, col = line_color)
}
```

```{r}
BEFORE_COLOR <- rgb(0, 0, 1, 0.3)
AFTER_COLOR <- rgb(1, 0, 0, 0.3)
```


```{r}
pdf("../report/graphs/transformations_hist.pdf", width = 25, height = 35)

par(mfrow = c(10, 4))
numeric_cols = colnames(voice)
numeric_cols = numeric_cols[!numeric_cols %in% c("id", "age", "gender", "accent")]
for (col in numeric_cols) {
  visualize_hist(voice[[col]], paste("Histogram of", col, "before transformation"), BEFORE_COLOR, "darkblue")
  # visualize_qq_plot(voice[[col]], paste("QQ Plot of", col, "before transformation"))
  visualize_hist(transformed_voice[[col]], paste("Histogram of", col, "after transformation"), AFTER_COLOR, "darkred")
  # visualize_qq_plot(transformed_voice[[col]], paste("QQ Plot of", col, "after transformation"))
}

dev.off()
```

```{r}

pdf("../report/graphs/transformations_qq.pdf", width = 25, height = 15)

par(mfrow = c(5, 8))
numeric_cols = colnames(voice)
numeric_cols = numeric_cols[!numeric_cols %in% c("id", "age", "gender", "accent")]
for (col in numeric_cols) {
  # visualize_hist(voice[[col]], paste("Histogram of", col, "before transformation"), BEFORE_COLOR, "darkblue")
  visualize_qq_plot(voice[[col]], paste("QQ Plot of", col, "before transformation"), BEFORE_COLOR, "darkblue")
  # visualize_hist(transformed_voice[[col]], paste("Histogram of", col, "after transformation"), AFTER_COLOR, "darkred")
  visualize_qq_plot(transformed_voice[[col]], paste("QQ Plot of", col, "after transformation"), AFTER_COLOR, "darkred")
}

dev.off()
```


## Correlation Matrix

```{r}
numeric_data <- transformed_voice[, numeric_cols]
correlation_matrix <- cor(numeric_data)
correlation_matrix
```

```{r}
library(corrplot)

plot_corr <- function(correlation_matrix) {
  corrplot(correlation_matrix, tl.col = "black")
}

pdf("../report/graphs/correlation_matrix.pdf", width = 7, height = 7)
plot_corr(correlation_matrix)
dev.off()

plot_corr(correlation_matrix)
```



