---
title: "DataTesting"
author: "Jin Qingyang"
knit: (function(inputFile, encoding) {
      out_dir <- "../docs/";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
output:
  html_document:
    theme: journal
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data

```{r}
male_data <- read.csv("../data/gender_sample/sampled_male_rows.csv")
female_data <- read.csv("../data/gender_sample/sampled_female_rows.csv")
head(male_data)
head(female_data)
```

## Q25

### F test

We first investigate whether the variance of Q25 is the same for both male and female

```{r}
male_q25 <- male_data$Q25
female_q25 <- female_data$Q25
var.test(male_q25, female_q25)
```
Since the p-value is less than 0.05, we reject the null hypothesis that the variance of Q25 is the same for male and female.
### Two sample t-test
We therefore conduct the two samle two sample test, under the assumption that the variance is not equal.

```{r}
t.test(male_q25, female_q25, var.equal = FALSE)
```

Since the p-value is less than 0.05, we reject the null hypothesis that the mean of Q25 is the same for both male, and female.
We would plot a boxplot to visualize the difference

```{r}
hist(male_q25, breaks = 100, col = "skyblue", main = "Histogram of Male Q25", xlab = "Values", ylim = c(0, max(hist(male_q25)$counts, hist(female_q25)$counts)))

hist(female_q25, breaks = 100, col = "pink", add = TRUE)

legend("topright", legend = c("Male", "Female"), fill = c("skyblue", "pink"))

```

## Q75
### F test

We first investigate whether the variance of Q75 is the same for both male and female

```{r}
male_q75 <- male_data$Q75
female_q75 <- female_data$Q75
var.test(male_q75, female_q75)
```
Since the p-value is more than 0.05, we do not reject the null hypothesis that the variance of Q75 is the same for male and female.
### Two sample t-test
We therefore conduct the two samle two sample test, under the assumption that the variance is equal.

```{r}
t.test(male_q75, female_q75, var.equal = TRUE)
```

Since the p-value is more than 0.05, we do not reject the null hypothesis that the mean of Q75 is the same for both male, and female.
We would plot a boxplot to visualize the difference

```{r}
hist(male_q75, breaks = 100, col = "skyblue", main = "Histogram of Male Q75", xlab = "Values", ylim = c(0, max(hist(male_q25)$counts, hist(female_q25)$counts)))

hist(female_q75, breaks = 100, col = "pink", add = TRUE)

legend("topright", legend = c("Male", "Female"), fill = c("skyblue", "pink"))

```