# Data Analysis

## Load Data

```{r}
data_path = "../data/train.csv"
data = read.csv(data_path)
head(data)
```

## `centroid`

We firstly load the data and draw a histogram of the `centroid` column.

```{r}
centroid = data$centroid
hist(centroid)
```

Then, we calculate the mean and standard deviation of the `centroid` column.

```{r}
centroid_mean <- mean(centroid)
centroid_sd <- sd(centroid)
print(paste("Mean of centroid:", centroid_mean))
print(paste("Standard deviation of centroid:", centroid_sd))
```

### Evaluate if the 'centroid' column follows a normal distribution

#### Histogram with overlaid normal curve

```{r}
hist(centroid, probability = TRUE, main = "Histogram of Centroid with Normal Curve", xlab = "Centroid")
curve(dnorm(x, mean = centroid_mean, sd = centroid_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

#### QQ plot

```{r}
qqnorm(centroid, main = "QQ Plot of Centroid")
qqline(centroid, col = "steelblue", lwd = 2)
```

### Log-transformed `centroid`

```{r}
centroid_log <- log(centroid)
hist(centroid_log, breaks = 80, main = "Histogram of log(centroid)", xlab = "log(centroid)")
centroid_log_mean <- mean(centroid_log)
centroid_log_sd <- sd(centroid_log)
print(paste("Mean of log-transformed centroid:", centroid_log_mean))
print(paste("Standard deviation of log-transformed centroid:", centroid_log_sd))
```

#### Histogram with overlaid normal curve

```{r}
hist(centroid_log, probability = TRUE, main = "Histogram of log-transformed Centroid with Normal Curve", xlab = "log(centroid)")
curve(dnorm(x, mean = centroid_log_mean, sd = centroid_log_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

#### QQ plot for log-transformed centroid

```{r}
qqnorm(centroid_log, main = "QQ Plot for log-transformed centroid")
qqline(centroid_log, col = "red")
```
