---
title: "Data Analysis"
knit: (function(inputFile, encoding) {
      out_dir <- "../docs/";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
output:
  html_document:
    theme: journal
    toc: true
    toc_float: true
---

## Load Data

```{r}
data_path = "../data/train.csv"
voice = read.csv(data_path)
head(voice)
```

## Centroid

We firstly load the data and draw a histogram of the `centroid` column.

```{r}
centroid = voice$centroid
hist(centroid)
```

Then, we calculate the mean and standard deviation of the `centroid` column.

```{r}
centroid_mean <- mean(centroid)
centroid_sd <- sd(centroid)
print(paste("Mean of centroid:", centroid_mean))
print(paste("Standard deviation of centroid:", centroid_sd))
```

#### Histogram with overlaid normal curve

```{r}
hist(centroid, probability = TRUE, main = "Histogram of Centroid with Normal Curve", xlab = "Centroid")
curve(dnorm(x, mean = centroid_mean, sd = centroid_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

#### QQ plot

```{r}
qqnorm(centroid, main = "QQ Plot of Centroid")
qqline(centroid, col = "steelblue", lwd = 2)
```

### Log-transformed `centroid`

```{r}
centroid_log <- log(centroid)
hist(centroid_log, breaks = 20, main = "Histogram of log(centroid)", xlab = "log(centroid)")
centroid_log_mean <- mean(centroid_log)
centroid_log_sd <- sd(centroid_log)
print(paste("Mean of log-transformed centroid:", centroid_log_mean))
print(paste("Standard deviation of log-transformed centroid:", centroid_log_sd))
```

#### Histogram with overlaid normal curve

```{r}
hist(centroid_log, probability = TRUE, main = "Histogram of log-transformed Centroid with Normal Curve", xlab = "log(centroid)")
curve(dnorm(x, mean = centroid_log_mean, sd = centroid_log_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

#### QQ plot for log-transformed `centroid`

```{r}
qqnorm(centroid_log, main = "QQ Plot for log-transformed centroid")
qqline(centroid_log, col = "red")
```

### Removing Outliers

```{r}
outliers <- !(centroid_log > (centroid_log_mean - 3 * centroid_log_sd) & centroid_log < (centroid_log_mean + 3 * centroid_log_sd))
outlier_ids <- data.frame(id = voice$id[outliers])
centroid_log_no_outliers <- centroid_log[!outliers]
```

Then, we save the IDs of the outliers to a CSV file.

```{r}
write.csv(outlier_ids, "../data/outliers/centroid.csv", row.names = FALSE)
```

Then, we draw the histogram and QQ plot for the log-transformed `centroid` column without the outliers.

```{r}
hist(centroid_log_no_outliers, breaks = 20, main = "Histogram of log-transformed Centroid without Outliers", xlab = "log(centroid)")
centroid_log_no_outliers_mean <- mean(centroid_log_no_outliers)
centroid_log_no_outliers_sd <- sd(centroid_log_no_outliers)
print(paste("Mean of log-transformed centroid without outliers:", centroid_log_no_outliers_mean))
print(paste("Standard deviation of log-transformed centroid without outliers:", centroid_log_no_outliers_sd))
```

```{r}
hist(centroid_log_no_outliers, probability = TRUE, main = "Histogram of log-transformed Centroid without Outliers with Normal Curve", xlab = "log(centroid)", breaks = 20)
curve(dnorm(x, mean = centroid_log_no_outliers_mean, sd = centroid_log_no_outliers_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(centroid_log_no_outliers, main = "QQ Plot for log-transformed centroid without outliers")
qqline(centroid_log_no_outliers, col = "red")
```

## MeanFun

```{r}
meanfun = voice$meanfun
hist(meanfun)
```

Then, we calculate the mean and standard deviation of the `meanfun` column.

```{r}
meanfun_mean <- mean(meanfun)
meanfun_sd <- sd(meanfun)
```

It is very obvious that the `meanfun` column is not normally distributed, we can see that from the histogram and QQ plot below.

```{r}
hist(meanfun, probability = TRUE, main = "Histogram of MeanFun with Normal Curve", xlab = "MeanFun", breaks = 20)
curve(dnorm(x, mean = meanfun_mean, sd = meanfun_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(meanfun, main = "QQ Plot of MeanFun")
qqline(meanfun, col = "steelblue", lwd = 2)
```

### Log-transformed `meanfun`

```{r}
meanfun_log <- log(meanfun)
hist(meanfun_log, breaks = 20, main = "Histogram of log(meanfun)", xlab = "log(meanfun)")
```

```{r}
meanfun_log_mean <- mean(meanfun_log)
meanfun_log_sd <- sd(meanfun_log)
print(paste("Mean of log-transformed meanfun:", meanfun_log_mean))
print(paste("Standard deviation of log-transformed meanfun:", meanfun_log_sd))
```

```{r}
hist(meanfun_log, probability = TRUE, main = "Histogram of log-transformed MeanFun with Normal Curve", xlab = "log(meanfun)", breaks = 20)
curve(dnorm(x, mean = meanfun_log_mean, sd = meanfun_log_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(meanfun_log, main = "QQ Plot for log-transformed meanfun")
qqline(meanfun_log, col = "red")
```

### Removing Outliers

```{r}
outliers <- !(meanfun_log > (meanfun_log_mean - 3 * meanfun_log_sd) & meanfun_log < (meanfun_log_mean + 3 * meanfun_log_sd))
outlier_ids <- data.frame(id = voice$id[outliers])
meanfun_log_no_outliers <- meanfun_log[!outliers]
```

Then, we save the IDs of the outliers to a CSV file.

```{r}
write.csv(outlier_ids, "../data/outliers/meanfun.csv", row.names = FALSE)
```

Then, we draw the histogram and QQ plot for the log-transformed `meanfun` column without the outliers.

```{r}
hist(meanfun_log_no_outliers, breaks = 20, main = "Histogram of log-transformed MeanFun without Outliers", xlab = "log(meanfun)")
meanfun_log_no_outliers_mean <- mean(meanfun_log_no_outliers)
meanfun_log_no_outliers_sd <- sd(meanfun_log_no_outliers)
print(paste("Mean of log-transformed meanfun without outliers:", meanfun_log_no_outliers_mean))
print(paste("Standard deviation of log-transformed meanfun without outliers:", meanfun_log_no_outliers_sd))
```

```{r}
hist(meanfun_log_no_outliers, probability = TRUE, main = "Histogram of log-transformed MeanFun without Outliers with Normal Curve", xlab = "log(meanfun)", breaks = 20)
curve(dnorm(x, mean = meanfun_log_no_outliers_mean, sd = meanfun_log_no_outliers_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(meanfun_log_no_outliers, main = "QQ Plot for log-transformed meanfun without outliers")
qqline(meanfun_log_no_outliers, col = "red")
```

 ### MeanDom
 ```{r}
meandom = voice$meandom
hist(meandom)
```

Then, we calculate the mean and standard deviation of the `meandom` column.

```{r}
meandom_mean <- mean(meandom)
meandom_sd <- sd(meandom)
```

We then draw the histogram and QQ plot for the `meandom` column to know more about its distribution.

```{r}
hist(meandom, probability = TRUE, main = "Histogram of MeanDom with Normal Curve", xlab = "MeanDom", breaks = 20)
curve(dnorm(x, mean = meandom_mean, sd = meandom_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(meandom, main = "QQ Plot of MeanDom")
qqline(meandom, col = "steelblue", lwd = 2)
```

### log-transformed `meandom`

```{r}
meandom_log <- log(meandom_log)
hist(meandom_log, breaks = as.integer(sqrt(length(meandom_log))), main = "Histogram of log(meandom)", xlab = "log(meandom)")
```

```{r}
meandom_log_mean <- mean(meandom_log)
meandom_log_sd <- sd(meandom_log)
print(paste("Mean of log-transformed meandom:", meandom_log_mean))
print(paste("Standard deviation of log-transformed meandom:", meandom_log_sd))
```

```{r}
hist(meandom_log, probability = TRUE, main = "Histogram of log-transformed MeanDom with Normal Curve", xlab = "log(meandom)", breaks = as.integer(sqrt(length(meandom_log))))
curve(dnorm(x, mean = meandom_log_mean, sd = meandom_log_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(meandom_log, main = "QQ Plot for log-transformed meandom")
qqline(meandom_log, col = "red")
```

### Removing Outliers

```{r}
outliers <- !(meandom_log > (meandom_log_mean - 3 * meandom_log_sd) & meandom_log < (meandom_log_mean + 3 * meandom_log_sd))
outlier_ids <- data.frame(id = voice$id[outliers])
meandom_log_no_outliers <- meandom_log[!outliers]
```

Then, we save the IDs of the outliers to a CSV file.

```{r}
write.csv(outlier_ids, "../data/outliers/meandom.csv", row.names = FALSE)
```

Then, we draw the histogram and QQ plot for the sqrt-transformed `meandom` column without the outliers.

```{r}
hist(meandom_log_no_outliers, breaks = as.integer(sqrt(length(meandom_log_no_outliers))), main = "Histogram of log-transformed MeanDom without Outliers", xlab = "log(meandom)")
meandom_log_no_outliers_mean <- mean(meandom_log_no_outliers)
meandom_log_no_outliers_sd <- sd(meandom_log_no_outliers)
print(paste("Mean of log-transformed meandom without outliers:", meandom_log_no_outliers_mean))
print(paste("Standard deviation of log-transformed meandom without outliers:", meandom_log_no_outliers_sd))
```

```{r}
hist(meandom_log_no_outliers, probability = TRUE, main = "Histogram of log-transformed MeanDom without Outliers with Normal Curve", xlab = "sqrt(meandom)", breaks = as.integer(sqrt(length(meandom_log_no_outliers))))
curve(dnorm(x, mean = meandom_log_no_outliers_mean, sd = meandom_log_no_outliers_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(meandom_log_no_outliers, main = "QQ Plot for log-transformed meandom without outliers")
qqline(meandom_log_no_outliers, col = "red")
```

### MinDom

```{r}
mindom = voice$mindom
hist(mindom)
```

Then, we calculate the mean and standard deviation of the `mindom` column.

```{r}
mindom_mean <- mean(mindom)
mindom_sd <- sd(mindom)
```

We then draw the histogram and QQ plot for the `mindom` column to know more about its distribution.

```{r}
hist(mindom, probability = TRUE, main = "Histogram of MinDom with Normal Curve", xlab = "MinDom", breaks = 20)
curve(dnorm(x, mean = mindom_mean, sd = mindom_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(mindom, main = "QQ Plot of MinDom")
qqline(mindom, col = "steelblue", lwd = 2)
```

### log-transformed `mindom`

```{r}
mindom_log <- log(mindom)
hist(mindom_log, breaks = as.integer(sqrt(length(mindom_log))), main = "Histogram of log(mindom)", xlab = "log(mindom)")
```

```{r}
mindom_log_mean <- mean(mindom_log)
mindom_log_sd <- sd(mindom_log)
print(paste("Mean of log-transformed mindom:", mindom_log_mean))
print(paste("Standard deviation of log-transformed mindom:", mindom_log_sd))
```

```{r}
hist(mindom_log, probability = TRUE, main = "Histogram of log-transformed MinDom with Normal Curve", xlab = "log(mindom)", breaks = as.integer(sqrt(length(mindom_log)))
curve(dnorm(x, mean = mindom_log_mean, sd = mindom_log_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(mindom_log, main = "QQ Plot for log-transformed mindom")
qqline(mindom_log, col = "red")
```

### Removing Outliers

```{r}
outliers <- !(mindom_log > (mindom_log_mean - 3 * mindom_log_sd) & mindom_log < (mindom_log_mean + 3 * mindom_log_sd))
outlier_ids <- data.frame(id = voice$id[outliers])
mindom_log_no_outliers <- mindom_log[!outliers]
```

Then, we save the IDs of the outliers to a CSV file.

```{r}
write.csv(outlier_ids, "../data/outliers/mindom.csv", row.names = FALSE)
```

Then, we draw the histogram and QQ plot for the sqrt-transformed `mindom` column without the outliers.

```{r}
hist(mindom_log_no_outliers, breaks = as.integer(sqrt(length(mindom_log_no_outliers))), main = "Histogram of log-transformed MinDom without Outliers", xlab = "log(mindom)")
mindom_log_no_outliers_mean <- mean(mindom_log_no_outliers)
mindom_log_no_outliers_sd <- sd(mindom_log_no_outliers)
print(paste("Mean of log-transformed mindom without outliers:", mindom_log_no_outliers_mean))
print(paste("Standard deviation of log-transformed mindom without outliers:", mindom_log_no_outliers_sd))
```

```{r}
hist(mindom_log_no_outliers, probability = TRUE, main = "Histogram of log-transformed MinDom without Outliers with Normal Curve", xlab = "sqrt(mindom)", breaks = as.integer(sqrt(length(mindom_log_no_outliers)))
curve(dnorm(x, mean = mindom_log_no_outliers_mean, sd = mindom_log_no_outliers_sd), col = "darkblue", lwd = 2, add = TRUE, yaxt = "n")
```

```{r}
qqnorm(mindom_log_no_outliers, main = "QQ Plot for log-transformed mindom without outliers")
qqline(mindom_log_no_outliers, col = "red")
```

### MaxDom

